PyQBench: a Python library for benchmarking gate-based quantum computers

### 2023-03-31 software_x_submission/manuscript.tex
Prepare files for software_x_submission

\begin{thebibliography}{00}
\bibitem{preskill} Preskill, J. (2018). Quantum Computing in the NISQ era and beyond. Quantum 2, 79.
\bibitem{rigetti} The web resource at \url{https://www.rigetti.com/}. Accessed on 2023-02-18.
\bibitem{ibmq} The web resource at \url{https://www.ibm.com/quantum}. Accessed on 2023-02-18.
\bibitem{oxforf} The web resource at \url{http://oxfordquantum.org/}. Accessed on 2023-02-18.
\bibitem{ionq} The web resource at \url{https://ionq.com/}. Accessed on 2023-02-18.
\bibitem{xanadu} The web resource at \url{https://www.xanadu.ai/}. Accessed on 2023-02-18.
\bibitem{dwave} The web resource at \url{https://www.dwavesys.com/}. Accessed on 2023-02-18.
\bibitem{quera} The web resource at \url{https://www.quera.com/}. Accessed on 2023-02-18.
\bibitem{sdk} The web resource at \url{https://docs.rigetti.com/qcs/}. Accessed on 2023-02-18.
\bibitem{pyquil} The web resource at \url{https://pyquil-docs.rigetti.com/en/stable/}. Accessed on 2023-02-18.
\bibitem{qiskit} The web resource at \url{https://qiskit.org/}. Accessed on 2023-02-18.
\bibitem{ibmqplatform} The web resource at \url{https://quantum-computing.ibm.com/}. Accessed on 2023-02-18.
\bibitem{amazon} The web resource at \url{https://aws.amazon.com/braket/}. Accessed on 2023-02-18.
\bibitem{zapata} The web resource at \url{https://www.zapatacomputing.com/orquestra-platform/}. Accessed on 2023-02-18.
\bibitem{preskillnew} Preskill, J. (2021). Quantum computing 40 years later. arXiv preprint arXiv:2106.10522.
\bibitem{liu2022sampling} 	Liu, Y., Otten, M., Bassirianjahromi, R., Jiang, L.,  Fefferman, B. (2021). Benchmarking near-term quantum computers via random circuit sampling. arXiv preprint arXiv:2105.05232.
\bibitem{knill2008randomized}
Knill, E., Leibfried, D., Reichle, R., Britton, J., Blakestad, R. B., Jost, J. D., Langer, C., Ozeri, R., Seidelin, S.,  Wineland, D. J. (2008). Randomized benchmarking of quantum gates. Physical Review A, 77(1), 012307.
\bibitem{wallman2014randomized} Wallman, J. J.,  Flammia, S. T. (2014). Randomized benchmarking with confidence. New Journal of Physics, 16(10), 103032.
\bibitem{helsen2022general} Helsen, J., Roth, I., Onorati, E., Werner, A. H.,  Eisert, J. (2022). General framework for randomized benchmarking. PRX Quantum, 3(2), 020357.
\bibitem{cornelissen2021scalable} Cornelissen, A., Bausch, J.,  Gilyén, A. (2021). Scalable benchmarks for gate-based quantum computers. arXiv preprint arXiv:2104.10698.
\bibitem{cross2019validating}
Cross, A. W., Bishop, L. S., Sheldon, S., Nation, P. D., Gambetta, J. M. (2019). Validating quantum computers using randomized model circuits. Physical Review A, 100(3), 032328.
\bibitem{moll2018quantum}
Moll, N., Barkoutsos, P., Bishop, L. S., Chow, J. M., Cross, A., Egger, D. J., Filipp, S., Fuhrer, A., Gambetta, J. M., Ganzhorn, M., Kandala, A., Mezzacapo, A., M{\"u}ller, P., Riess, W., Salis, G., Smolin, J., Tavernelli, I.,  Temme, K. (2018). Quantum optimization using variational algorithms on near-term quantum devices. Quantum Science and Technology, 3(3), 030503.
\bibitem{pelofske2022volume} Pelofske, E., Bärtschi, A.,  Eidenbenz, S. (2022). Quantum volume in practice: What users can expect from NISQ devices. IEEE Transactions on Quantum Engineering, 3, 1-19.
	\bibitem{mqt2022} Quetschlich, N., Burgholzer, L., Wille, R. (2022). MQT Bench: Benchmarking software and design automation tools for quantum computing. arXiv preprint arXiv:2204.13719.
\bibitem{mqt-bench} The web resource at  \url{https://github.com/cda-tum/MQTBench}. Accessed on 2023-02-18.
	\bibitem{supermarq} Tomesh, T., Gokhale, P., Omole, V., Ravi, G. S., Smith, K. N., Viszlai, J., Wu, X.,  Hardavellas, N., Martonosi, M.R.,  Chong, F. T. (2022). Supermarq: A scalable quantum benchmark suite. In 2022 IEEE International Symposium on High-Performance Computer Architecture (HPCA) (pp. 587-603). IEEE.
\bibitem{supermarkq-github} The web resource at \url{https://github.com/SupertechLabs/SupermarQ}. Accessed on 2023-02-18.
\bibitem{qiskit-randomized} The web resource at
\url{https://github.com/qiskit-community/qiskit-benchmarks}. Accessed on 2023-02-18.
\bibitem{forest-benchmarking} The web resource at \url{https://github.com/rigetti/forest-benchmarking}. Accessed on 2023-02-18.
\bibitem{volume-in-practice} The web resource at \url{https://github.com/lanl/Quantum-Volume-in-Practice}. Accessed on 2023-02-18.
\bibitem{cross-entropy-bench} The web resource at
\url{https://quantumai.google/cirq/noise/qcvv/xeb_theory}.  Accessed on 2023-02-18.
\bibitem{puchala2018strategies} Puchała, Z.,  Pawela, Ł.,  Krawiec, A.,  Kukulski, R. (2018). Strategies for
optimal single-shot discrimination of quantum measurements. Physical Review A
98.4, 042103.
\bibitem{watrous} Watrous, J. (2018). The theory of quantum information. Cambridge University Press.
\bibitem{helstrom1976quantum} Helstrom, C. W. (1969). Quantum detection and estimation theory. Journal of Statistical Physics, 1(2), 231-252.
\bibitem{yaml} The web resource at \url{https://yaml.org/spec/1.2.2/}. Accessed on 2023-02-18.
\bibitem{pyqbenchgithub} The web resource at \url{https://github.com/iitis/PyQBench}. Accessed on 2023-02-18.
\bibitem{pyqbenchgithub} The web resource at \url{https://github.com/iitis/PyQBench}. Accessed on 2023-02-18.
\bibitem{pyqbenchdocs} The web resource at \url{https://pyqbench.readthedocs.io/en/latest/}. Accessed on 2023-02-18.
\bibitem{qiskit-braket-provider} The web resource at \url{https://aws.amazon.com/blogs/quantum-computing/introducing-the-qiskit-provider-for-amazon-braket/}. Accessed on 2023-02-18.
\bibitem{qiskit-braket-provider-github} The web resource at \url{https://github.com/qiskit-community/qiskit-braket-provider}. Accessed on 2023-02-18.
\bibitem{aer} The web resource at \url{https://github.com/Qiskit/qiskit-aer}. Accessed on 2023-02-18.
\bibitem{mthree} The web resource at \url{https://qiskit.org/documentation/partners/mthree/stubs/mthree.M3Mitigation.html}. Accessed on 2023-02-10.
\bibitem{mthreepublication} Nation, P. D., Kang, H., Sundaresan, N.,  Gambetta, J. M. (2021). Scalable mitigation of measurement errors on quantum computers. PRX Quantum, 2(4), 040326.
\bibitem{numericalrangle} Murnaghan, F. D. (1932). On the field of values of a square matrix. Proceedings of the National Academy of Sciences, 18(3), 246-248.
\bibitem{nr} The web resource at \url{https://numericalshadow.org/}. Accessed on 2022-10-02.
\bibitem{watrous2021simplier} Watrous, J. (2013). Simpler semidefinite programs for completely bounded norms. Chicago Journal of Theoretical Computer Science, 8.
\bibitem{lewandowska2021certification} Lewandowska, P., Krawiec, A., Kukulski, R., Pawela, Ł.,  Puchała, Z. (2021). On the optimal certification of von Neumann measurements. Scientific Reports, 11(1), 3623.
\bibitem{hausdorff} Hausdorff, F. (1919). Der wertvorrat einer bilinearform. Mathematische Zeitschrift, 3(1), 314-316.
\bibitem{toeplitz} Toeplitz, O. (1918). Das algebraische Analogon zu einem Satze von Fejér. Mathematische Zeitschrift, 2(1-2), 187-197.
\bibitem{michielsen2017benchmarking} Michielsen, K., Nocon, M., Willsch, D., Jin, F., Lippert, T.,  De Raedt, H. (2017). Benchmarking gate-based quantum computers. Computer Physics Communications, 220, 44-55.
\bibitem{zhukov2019quantum} Zhukov, A. A., Kiktenko, E. O., Elistratov, A. A., Pogosov, W. V.,  Lozovik, Y. E. (2019). Quantum communication protocols as a benchmark for programmable quantum computers. Quantum Information Processing, 18(1), 31.
\bibitem{hamilton2018generative} Hamilton, Kathleen E., Eugene F. Dumitrescu,
and Raphael C. Pooser. (2019). Generative model benchmarks for superconducting
qubits. Physical Review A 99(6), 062323.
\bibitem{benedetti2018generative} Benedetti, M., Garcia-Pintos, D., Perdomo, O., Leyton-Ortega, V., Nam, Y., Perdomo-Ortiz, A. (2019). A generative modeling approach for benchmarking and training shallow quantum circuits. npj Quantum Information, 5(1), 45.

\end{thebibliography}

>>>>

% \begin{thebibliography}{00}
% \bibitem{preskill} Preskill, J. (2018). Quantum Computing in the NISQ era and beyond. Quantum 2, 79.
% \bibitem{rigetti} The web resource at \url{https://www.rigetti.com/}. Accessed on 2023-02-18.
% \bibitem{ibmq} The web resource at \url{https://www.ibm.com/quantum}. Accessed on 2023-02-18.
% \bibitem{oxforf} The web resource at \url{http://oxfordquantum.org/}. Accessed on 2023-02-18.
% \bibitem{ionq} The web resource at \url{https://ionq.com/}. Accessed on 2023-02-18.
% \bibitem{xanadu} The web resource at \url{https://www.xanadu.ai/}. Accessed on 2023-02-18.
% \bibitem{dwave} The web resource at \url{https://www.dwavesys.com/}. Accessed on 2023-02-18.
% \bibitem{quera} The web resource at \url{https://www.quera.com/}. Accessed on 2023-02-18.
% \bibitem{sdk} The web resource at \url{https://docs.rigetti.com/qcs/}. Accessed on 2023-02-18.
% \bibitem{pyquil} The web resource at \url{https://pyquil-docs.rigetti.com/en/stable/}. Accessed on 2023-02-18.
% \bibitem{qiskit} The web resource at \url{https://qiskit.org/}. Accessed on 2023-02-18.
% \bibitem{ibmqplatform} The web resource at \url{https://quantum-computing.ibm.com/}. Accessed on 2023-02-18.
% \bibitem{amazon} The web resource at \url{https://aws.amazon.com/braket/}. Accessed on 2023-02-18.
% \bibitem{zapata} The web resource at \url{https://www.zapatacomputing.com/orquestra-platform/}. Accessed on 2023-02-18.
% \bibitem{preskillnew} Preskill, J. (2021). Quantum computing 40 years later. arXiv preprint arXiv:2106.10522.
% \bibitem{liu2022sampling} 	Liu, Y., Otten, M., Bassirianjahromi, R., Jiang, L.,  Fefferman, B. (2021). Benchmarking near-term quantum computers via random circuit sampling. arXiv preprint arXiv:2105.05232.
% \bibitem{knill2008randomized}
% Knill, E., Leibfried, D., Reichle, R., Britton, J., Blakestad, R. B., Jost, J. D., Langer, C., Ozeri, R., Seidelin, S.,  Wineland, D. J. (2008). Randomized benchmarking of quantum gates. Physical Review A, 77(1), 012307.
% \bibitem{wallman2014randomized} Wallman, J. J.,  Flammia, S. T. (2014). Randomized benchmarking with confidence. New Journal of Physics, 16(10), 103032.
% \bibitem{helsen2022general} Helsen, J., Roth, I., Onorati, E., Werner, A. H.,  Eisert, J. (2022). General framework for randomized benchmarking. PRX Quantum, 3(2), 020357.
% \bibitem{cornelissen2021scalable} Cornelissen, A., Bausch, J.,  Gilyén, A. (2021). Scalable benchmarks for gate-based quantum computers. arXiv preprint arXiv:2104.10698.
% \bibitem{cross2019validating}
% Cross, A. W., Bishop, L. S., Sheldon, S., Nation, P. D., Gambetta, J. M. (2019). Validating quantum computers using randomized model circuits. Physical Review A, 100(3), 032328.
% \bibitem{moll2018quantum}
% Moll, N., Barkoutsos, P., Bishop, L. S., Chow, J. M., Cross, A., Egger, D. J., Filipp, S., Fuhrer, A., Gambetta, J. M., Ganzhorn, M., Kandala, A., Mezzacapo, A., M{\"u}ller, P., Riess, W., Salis, G., Smolin, J., Tavernelli, I.,  Temme, K. (2018). Quantum optimization using variational algorithms on near-term quantum devices. Quantum Science and Technology, 3(3), 030503.
% \bibitem{pelofske2022volume} Pelofske, E., Bärtschi, A.,  Eidenbenz, S. (2022). Quantum volume in practice: What users can expect from NISQ devices. IEEE Transactions on Quantum Engineering, 3, 1-19.
% 	\bibitem{mqt2022} Quetschlich, N., Burgholzer, L., Wille, R. (2022). MQT Bench: Benchmarking software and design automation tools for quantum computing. arXiv preprint arXiv:2204.13719.
% \bibitem{mqt-bench} The web resource at  \url{https://github.com/cda-tum/MQTBench}. Accessed on 2023-02-18.
% 	\bibitem{supermarq} Tomesh, T., Gokhale, P., Omole, V., Ravi, G. S., Smith, K. N., Viszlai, J., Wu, X.,  Hardavellas, N., Martonosi, M.R.,  Chong, F. T. (2022). Supermarq: A scalable quantum benchmark suite. In 2022 IEEE International Symposium on High-Performance Computer Architecture (HPCA) (pp. 587-603). IEEE.
% \bibitem{supermarkq-github} The web resource at \url{https://github.com/SupertechLabs/SupermarQ}. Accessed on 2023-02-18.
% \bibitem{qiskit-randomized} The web resource at
% \url{https://github.com/qiskit-community/qiskit-benchmarks}. Accessed on 2023-02-18.
% \bibitem{forest-benchmarking} The web resource at \url{https://github.com/rigetti/forest-benchmarking}. Accessed on 2023-02-18.
% \bibitem{volume-in-practice} The web resource at \url{https://github.com/lanl/Quantum-Volume-in-Practice}. Accessed on 2023-02-18.
% \bibitem{cross-entropy-bench} The web resource at
% \url{https://quantumai.google/cirq/noise/qcvv/xeb_theory}.  Accessed on 2023-02-18.
% \bibitem{puchala2018strategies} Puchała, Z.,  Pawela, Ł.,  Krawiec, A.,  Kukulski, R. (2018). Strategies for
% optimal single-shot discrimination of quantum measurements. Physical Review A
% 98.4, 042103.
% \bibitem{watrous} Watrous, J. (2018). The theory of quantum information. Cambridge University Press.
% \bibitem{helstrom1976quantum} Helstrom, C. W. (1969). Quantum detection and estimation theory. Journal of Statistical Physics, 1(2), 231-252.
% \bibitem{yaml} The web resource at \url{https://yaml.org/spec/1.2.2/}. Accessed on 2023-02-18.
% \bibitem{pyqbenchgithub} The web resource at \url{https://github.com/iitis/PyQBench}. Accessed on 2023-02-18.
% \bibitem{pyqbenchgithub} The web resource at \url{https://github.com/iitis/PyQBench}. Accessed on 2023-02-18.
% \bibitem{pyqbenchdocs} The web resource at \url{https://pyqbench.readthedocs.io/en/latest/}. Accessed on 2023-02-18.
% \bibitem{qiskit-braket-provider} The web resource at \url{https://aws.amazon.com/blogs/quantum-computing/introducing-the-qiskit-provider-for-amazon-braket/}. Accessed on 2023-02-18.
% \bibitem{qiskit-braket-provider-github} The web resource at \url{https://github.com/qiskit-community/qiskit-braket-provider}. Accessed on 2023-02-18.
% \bibitem{aer} The web resource at \url{https://github.com/Qiskit/qiskit-aer}. Accessed on 2023-02-18.
% \bibitem{mthree} The web resource at \url{https://qiskit.org/documentation/partners/mthree/stubs/mthree.M3Mitigation.html}. Accessed on 2023-02-10.
% \bibitem{mthreepublication} Nation, P. D., Kang, H., Sundaresan, N.,  Gambetta, J. M. (2021). Scalable mitigation of measurement errors on quantum computers. PRX Quantum, 2(4), 040326.
% \bibitem{numericalrangle} Murnaghan, F. D. (1932). On the field of values of a square matrix. Proceedings of the National Academy of Sciences, 18(3), 246-248.
% \bibitem{nr} The web resource at \url{https://numericalshadow.org/}. Accessed on 2022-10-02.
% \bibitem{watrous2021simplier} Watrous, J. (2013). Simpler semidefinite programs for completely bounded norms. Chicago Journal of Theoretical Computer Science, 8.
% \bibitem{lewandowska2021certification} Lewandowska, P., Krawiec, A., Kukulski, R., Pawela, Ł.,  Puchała, Z. (2021). On the optimal certification of von Neumann measurements. Scientific Reports, 11(1), 3623.
% \bibitem{hausdorff} Hausdorff, F. (1919). Der wertvorrat einer bilinearform. Mathematische Zeitschrift, 3(1), 314-316.
% \bibitem{toeplitz} Toeplitz, O. (1918). Das algebraische Analogon zu einem Satze von Fejér. Mathematische Zeitschrift, 2(1-2), 187-197.
% \bibitem{michielsen2017benchmarking} Michielsen, K., Nocon, M., Willsch, D., Jin, F., Lippert, T.,  De Raedt, H. (2017). Benchmarking gate-based quantum computers. Computer Physics Communications, 220, 44-55.
% \bibitem{zhukov2019quantum} Zhukov, A. A., Kiktenko, E. O., Elistratov, A. A., Pogosov, W. V.,  Lozovik, Y. E. (2019). Quantum communication protocols as a benchmark for programmable quantum computers. Quantum Information Processing, 18(1), 31.
% \bibitem{hamilton2018generative} Hamilton, Kathleen E., Eugene F. Dumitrescu,
% and Raphael C. Pooser. (2019). Generative model benchmarks for superconducting
% qubits. Physical Review A 99(6), 062323.
% \bibitem{benedetti2018generative} Benedetti, M., Garcia-Pintos, D., Perdomo, O., Leyton-Ortega, V., Nam, Y., Perdomo-Ortiz, A. (2019). A generative modeling approach for benchmarking and training shallow quantum circuits. npj Quantum Information, 5(1), 45.

% \end{thebibliography}

\bibliographystyle{unsrt}
\bibliography{references}
